---
title: 'GLM Assignment : Poisson and Binomial'
subtitle: Trevor Walker
output:
  html_document:
    df_print: paged
---
```{r setup2, include=FALSE}
#lapply(packages_needed, require, character.only = TRUE)
library(ggplot2)
library(plyr)
library(MASS)
library(dplyr)
library(ggfortify)
```
First I need to read in data

```{r Data, include=TRUE}
Bat_M.A_Data<- read.csv("Data/GLM_Assignment_2.csv")

Bat_M.A_Data
```
My First GLM using the poisson family because I'm looking at discrete count data.

```{r glm 1, include=TRUE}
Bat_NetVSAcoust.glm<- glm(Net_Species_Richness~ Acoustic_Species_Richness, data=Bat_M.A_Data , family= poisson(link = "log"))


```
View the plot

```{r plot 1, include=TRUE}

Bat_NetVSAcoust.plot<- ggplot(Bat_NetVSAcoust.glm, aes(Acoustic_Species_Richness, Net_Species_Richness)) + 
  geom_point(size=3) +stat_smooth(method = glm, method.args = list(family = poisson(link = "log"))) +
  labs(title="GLM Family= Poisson, Bat Acoustics VS. Mist-net Numbers") +
  xlab ("Acoustic # of Species") +
  ylab ("MistNet # of Species")

Bat_NetVSAcoust.plot


```
Next We can View the Autoplot
```{r autoplot 1, include=TRUE}
autoplot(Bat_NetVSAcoust.glm)
```

```{r Anova and summary 1, include=TRUE}
anova(Bat_NetVSAcoust.glm)

summary(Bat_NetVSAcoust.glm)
```
Here We can see there is no statistical significance of the acoustic data of Species Richness detected with the species richness detected via mist netting.


Next We will look at the presence or absence of the Big Brown Bat (EPFU) by looking at Site Quality

```{r GLM Binomial, include=TRUE}
EPFU_OccuranceVSSite_Quality.glm<- glm(EPFU_Occurance~ Visual_Score, data=Bat_M.A_Data , family= binomial(link = "logit"))

```
Then we will view the plot
```{r plot 2}
EPFU_OccuranceVSSite_Quality.plot<- ggplot(EPFU_OccuranceVSSite_Quality.glm, aes(Visual_Score, EPFU_Occurance)) + 
  geom_point(size=3) +stat_smooth(method = glm, method.args = list(family = binomial)) +
  labs(title="GLM Family= Binomial,  EPFU Occurance by Site Visual Quality") +
  xlab ("Site Quality Category") +
  ylab ("Probability of EPFU Occurance")

EPFU_OccuranceVSSite_Quality.plot
```

The autoplot
```{r autoplot 2}
autoplot(EPFU_OccuranceVSSite_Quality.glm)
```

Next we look at the summary

```{r Interaction Plot}
anova(EPFU_OccuranceVSSite_Quality.glm)

summary(EPFU_OccuranceVSSite_Quality.glm)
```
For Every increase in Site Quality Score the Probability of an EPFU occurance increases.


